---
title: "Shiny"
author: "Jordan Stout"
date: "11-15-2024"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(reactable)
library(vroom)
library(tidyverse)
```

2.3.5

1
renderPrint(summary(mtcars))  ->  verbatimTextOutput

renderText("Good morning!")   ->  TextOutput

renderPrint(t.test(1:5, 2:6))  ->  verbatimTextOutput

renderText(str(lm(mpg ~ wt, data = mtcars)))  ->  verbatimTextOutput

2
```{r}
ui <- fluidPage(
    plotOutput("plot", width = "700px", height = "300px")
)

server <- function(input, output, session) {
    output$plot <- renderPlot(plot(1:5), res = 96, alt = "Scatterplot of 5 Numbers")
}

shinyApp(ui, server)
```
3
```{r}
ui <- fluidPage(
    dataTableOutput("table")
)

server <- function(input, output, session) {
    output$table <- renderDataTable(mtcars, options = list(pageLength = 5, ordering = FALSE, searching = FALSE))
}

shinyApp(ui, server)
```

4
```{r}
ui <- fluidPage(
  reactableOutput("table")
)

server <- function(input, output) {
  output$table <- renderReactable({reactable(mtcars)})
}

shinyApp(ui, server)
```



3.3.6

1
```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
```

input has to become output
name has to become input$name
```{r}
server1 <- function(input, output, server) {
  output$greeting <- renderText(paste0("Hello ", input$name))
}
```

make greeting a reactive and add parenthesis
```{r}
server2 <- function(input, output, server) {
  greeting <- reactive(paste0("Hello ", input$name))
  output$greeting <- renderText(greeting())
}
```

missing renderText() and typo
```{r}
server3 <- function(input, output, server) {
  output$greeting <- renderText(paste0("Hello ", input$name))
}
```

2
server1
a -|
   |- c-|
b -|    |
        |-e-f
d-------|

server2
x1 -|
x2 -|--x-|
x3 -|    |
         |--z
y1 -|--y-|
y2 -|

server3
a--a--b--c--d
      |  |  |
b-----|  |  |
         |  |
c--------|  |
            |
d-----------|


3
it won't work because range and var are reserved words in base R


4.8
```{r}

```





